ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2017-05-31 answer-to-reviewers.tex

\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}

%\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage{timesmt}

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{tikz}
%\usetikzlibrary{shapes.misc,fit}
\usetikzlibrary{%
   arrows,%
   calc,%
   fit,%
   patterns,%
   plotmarks,%
   shapes.geometric,%
   shapes.misc,%
   shapes.symbols,%
   shapes.arrows,%
   shapes.callouts,%
   shapes.multipart,%
   shapes.gates.logic.US,%
   shapes.gates.logic.IEC,%
   er,%
   automata,%
   backgrounds,%
   chains,%
   topaths,%
   trees,%
   petri,%
   mindmap,%
   matrix,%
   calendar,%
   folding,%
   fadings,%
   through,%
   patterns,%
   positioning,%
   scopes,%
   decorations.fractals,%
   decorations.shapes,%
   decorations.text,%
   decorations.pathmorphing,%
   decorations.pathreplacing,%
   decorations.footprints,%
   decorations.markings,%
   shadows}

\usepackage{lineno} % comment this out to get line number again
%\usepackage{hyperref}
\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\dd}{\,\mathrm{d}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Rsys{R_\text{sys}}
\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}
\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution

\newcommand{\El}{\ul{\operatorname{E}}}
\newcommand{\Eu}{\ol{\operatorname{E}}}

\def\yz{y\uz}
\def\yn{y\un}
%\def\yi{y\ui}
\newcommand{\yfun}[1]{y^{({#1})}}
\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}

\def\ykz{y\uz_k}
\def\ykn{y\un_k}

\def\yzl{\ul{y}\uz}
\def\yzu{\ol{y}\uz}
\def\ynl{\ul{y}\un}
\def\ynu{\ol{y}\un}
\def\yil{\ul{y}\ui}
\def\yiu{\ol{y}\ui}

\def\ykzl{\ul{y}\uz_k}
\def\ykzu{\ol{y}\uz_k}
\def\yknl{\ul{y}\un_k}
\def\yknu{\ol{y}\un_k}

\newcommand{\ykzfun}[1]{y\uz_{#1}}
\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}

\def\nz{n\uz}
\def\nn{n\un}
%\def\ni{n\ui}
\newcommand{\nfun}[1]{n^{({#1})}}
\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}
\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}

\def\nzl{\ul{n}\uz}
\def\nzu{\ol{n}\uz}
\def\nnl{\ul{n}\un}
\def\nnu{\ol{n}\un}
\def\nil{\ul{n}\ui}
\def\niu{\ol{n}\ui}

\def\nkzl{\ul{n}\uz_k}
\def\nkzu{\ol{n}\uz_k}
\def\nknl{\ul{n}\un_k}
\def\nknu{\ol{n}\un_k}

\def\taut{\tau(\vec{t})}
\def\ttau{\tilde{\tau}}
\def\ttaut{\ttau(\vec{t})}

\def\MZ{\mathcal{M}\uz}
\def\MN{\mathcal{M}\un}

\def\MkZ{\mathcal{M}\uz_k}
\def\MkN{\mathcal{M}\un_k}

\def\PkZ{\Pi\uz_k}
\def\PkN{\Pi\un_k}
\newcommand{\PZi}[1]{\Pi\uz_{#1}}

\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\newcommand{\comments}[1]{{\small\color{gray} #1}}

\newtheorem{example}{Example}

\allowdisplaybreaks

\begin{document}
\title{RESPONSE TO REVIEWERS' COMMENTS TO OUR MANUSCRIPT RUENG-211}

\author{
Gero Walter%
\thanks{
Postdoctoral Researcher,
School of Industrial Engineering,
Eindhoven University of Technology, Eindhoven, The Netherlands.
E-mail: g.m.walter@tue.nl. Corresponding author.},
\ Ph.D.
\\
and
Frank P.A. Coolen%
\thanks{
Professor,
Department of Mathematical Sciences,
Durham University, Durham, United Kingdom.
E-mail: frank.coolen@durham.ac.uk.},
\ Ph.D.
}

\maketitle

\begin{abstract}
We would like to thank the two anonymous reviewers for their detailed and constructive comments,
and their overall positive votum.
We reproduce their comments here verbatim,
and have numbered the reviewers' comments and questions to allow for easy referencing. 
Our answers are interlaced and typeset in \emph{italic}.
\end{abstract}

\section{Reviewer 1}

\section{Reviewer 2}

\end{document}

### 2017-05-31 answer-to-reviewers.tex

%\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}

@@

\author{
Gero Walter%
\thanks{
Postdoctoral Researcher,
School of Industrial Engineering,
Eindhoven University of Technology, Eindhoven, The Netherlands.
E-mail: g.m.walter@tue.nl. Corresponding author.},
\ Ph.D.
\\
and
Frank P.A. Coolen%
\thanks{
Professor,
Department of Mathematical Sciences,
Durham University, Durham, United Kingdom.
E-mail: frank.coolen@durham.ac.uk.},
\ Ph.D.
}

\maketitle

\begin{abstract}
We would like to thank the two anonymous reviewers for their detailed and constructive comments,
and their overall positive votum.
We reproduce their comments here verbatim,
and have numbered the reviewers' comments and questions to allow for easy referencing. 
Our answers are interlaced and typeset in \emph{italic}.
\end{abstract}

\section*{Reviewer 1}

The authors presented an approach to mitigate the issue of prior-data conflict.
The idea is to consider sets of prior distributions to model limited knowledge on Weibull distributed component lifetimes,
and then to model the systems with arbitrary layout using the survival signature.
As mentioned by the authors the calculation of lower and upper predictive system reliability bounds is tractable.

\smallskip

\emph{***Drop notion of `mitigate', replace with `highlight' / etc? (appears in abstract and end of introduction only) ***\\
We present a method that explicitly shows, through imprecision in the inferences, when prior and data vary substantially.}

The manuscript is well written, clear and complete. The manuscript is ready to be published.
However, the authors might want to consider to comment about:
\begin{enumerate}
\item how this approach performs compared with existing and traditional approaches

\smallskip

\empħ{We discuss our changes related to existing and traditional approaches in the answers to Reviewer 2's comments below.}

\item are any numerical approaches that can be used to perform system reliability based on the survival signature
or consider arbitrary distributions for the component failure time?
\smallskip

\empħ{We are not sure if we have understood this comment well.
The survival signature allows to calculate the system reliability for arbitrary component lifetime distributions,
as is clear from Equation~(13), this is explained in detail in the cited reference (Coolen and Coolen-Maturi 2012).
We have added a sentence to emphasize this fact.}
\end{enumerate}

Furthermore, at page 15 the authors make a statement that this method has been implemented in R
and it is intended to be released as a package. Is the code already available?

\section*{Reviewer 2}

### 2017-05-31 asce-paper.tex
changes for arxiv submission
setup answer to reviewers
comments reviewer 1 part 1

%\usepackage{hyperref}
%\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

@@

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

The paper is organized as follows.
In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter is described,
illustrating the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
%is transfomed to the necessary form for use within the survival signature framework,
%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components.
Section~\ref{sec:examples} contains examples illustrating the merits of our method,
by studying the effect of surprisingly early or late component failures,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.
Section~\ref{sec:concluding} concludes the paper by summarizing results
and indicating avenues for further research.

@@

\section{Robust Reliability for Complex Systems via the Survival Signature}
\label{sec:robrel}

@@

The survival signature \cite{2012:survsign} is a summary of the structure function
for systems with $K$ groups of exchangeable components.
Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
it is defined as the probability for the event that the system functions
given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
%System survival calculated by %(see Risk Analysis paper eq. (7))
\begin{linenomath*}
\begin{align}
P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
%\intertext{ and assuming components of different types are independent,}
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
\label{eq:sysrel-survsign}
\end{align}
\end{linenomath*}
where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
and the last equality holds as we assume that components of different types are independent.
Note that for coherent systems,
the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
%
%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
%\begin{linenomath*}
%\begin{align}
%P(C^k_t = l_k\mid\nkz,\ykz)
% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
%\end{align}
%\end{linenomath*}
%under the assumption that components of the same type are independent given $\lambda_k$.

@@

\section{Concluding Remarks}
\label{sec:concluding}

>>>>

\usepackage{lineno} % comment this out to get line number again
%\usepackage{hyperref}
\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

@@

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate/highlight*** this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

The paper is organized as follows.
In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
with fixed shape parameter is described,
illustrating the issue of prior-data conflict.
Section~\ref{sec:modforsurpr} then details the use of sets of priors
for the scale parameter $\lambda_k$ of the Weibull distribution,
showing how this mitigates / highlights*** the prior-data conflict issue for $\lambda_k$.
Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
for a running system based on sets of priors for $\lambda_k$. 
%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
%is transfomed to the necessary form for use within the survival signature framework,
%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
Section~\ref{sec:elicitation} discusses elicitation,
by giving guidelines on how to choose prior parameter bounds
that reflect expert information on components.
Section~\ref{sec:examples} contains examples illustrating the merits of our method,
by studying the effect of surprisingly early or late component failures,
showing that observations in conflict to prior assumptions
indeed lead to more cautious system reliability predictions.
Section~\ref{sec:concluding} concludes the paper by summarizing results
and indicating avenues for further research.

@@

\newpage
\section{Robust Reliability for Complex Systems via the Survival Signature}
\label{sec:robrel}

@@

The survival signature \cite{2012:survsign} is a summary of the structure function
for systems with $K$ groups of exchangeable components.
Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
it is defined as the probability for the event that the system functions
given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
%System survival calculated by %(see Risk Analysis paper eq. (7))
\begin{linenomath*}
\begin{align}
P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
%\intertext{ and assuming components of different types are independent,}
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
\label{eq:sysrel-survsign}
\end{align}
\end{linenomath*}
where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
and the last equality holds as we assume that components of different types are independent.
Equation~\ref{eq:sysrel-survsign} shows that the survival signature allows to calculate the system reliability $P(\Tsys > t)$
for arbitrary component failure time distributions,
as the probabilities $P(C^k_t = l_k)$ can be determined from any failure time distribution.
Note that for coherent systems,
the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.

%
%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
%\begin{linenomath*}
%\begin{align}
%P(C^k_t = l_k\mid\nkz,\ykz)
% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
%\end{align}
%\end{linenomath*}
%under the assumption that components of the same type are independent given $\lambda_k$.

@@

\newpage
\section{Concluding Remarks}
\label{sec:concluding}
